Predicting Spotify Audio Features from Last.fm Tags

### 2023-07-01 paper/main.tex
fix authors

\author*[1]{\fnm{Jaime} \sur{Ramírez Castillo}}\email{Jaime.Ramirez@alu.uclm.es}

@@

>>>>

\author*[1]{\fnm{Jaime} \sur{Ramírez Castillo}}\email{Jaime.Ramirez@alu.uclm.es}
\equalcont{These authors contributed equally to this work.}

@@

\author[2]{\fnm{Philippe} \sur{Leray}}\email{philippe.leray@univ-nantes.fr}

\affil*[1]{\orgdiv{Departamento de Sistemas Informáticos}, \orgname{Universidad de Castilla-La Mancha}, \orgaddress{\street{Campus universitario s/n}, \city{Albacete}, \postcode{02071}, \country{Spain}}}

\affil[2]{\orgdiv{Laboratoire des Sciences du Numérique de Nantes}, \orgname{Centre national de la recherche scientifique, University of Nantes}, \orgaddress{\city{Nantes}, \country{France}}}
